\textbf{\sc Deliberative Autonomy for Marine Robotics}

### 2012-01-30 trunk/europa.tex
checkpoint. more europa content.

Below is an example of a random positioning of queens on a NxN chessboard. Queens in violation of the non-attack constraint are highlighted in red.
TODO: include figure.

@@

TODO: include figure

@@

Below is an example of a a solution provided by EUROPA for an RCPSP instance with 10 activities, 5 resources and 30 temporal constraints.
TODO: include figure

@@

TODO: include figure

As we can see, a planning problem (what actions must be performed to achieve a goal) may embed a scheduling problem (in what order should those actions be performed), and both embed Constraint Satisfaction problems as temporal, resource and many other kinds of constraints must be respected in most real life problems.

@@

(TODO: add figure)

>>>>

Below is an example of a random positioning of queens on a NxN chessboard. Queens in violation of the non-attack constraint are highlighted in red.

\begin{figure}
\centering
\includegraphics[scale=0.35]{figs/Example-NQueens0.jpg}
\caption{\small N-Queens problem}
\label{fig:nqueens-1}
\vskip+0.1cm
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.35]{figs/Example-NQueens1.jpg}
\caption{\small N-Queens solution}
\label{fig:nqueens-2}
\vskip+0.1cm
\end{figure}

@@

Below is an example of a a solution provided by EUROPA for an RCPSP instance with 10 activities, 5 resources and 30 temporal constraints.

\begin{figure}
\centering
\includegraphics[scale=0.35]{figs/Example-UBO0.jpg}
\caption{\small RCPSP problem}
\label{fig:rcpsp-1}
\vskip+0.1cm
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.35]{figs/Example-Shopping0.jpg}
\caption{\small Shopping Agent problem}
\label{fig:shopping-1}
\vskip+0.1cm
\end{figure}

As we can see, a planning problem (what actions must be performed to achieve a goal) may embed a scheduling problem (in what order should those actions be performed), and both embed Constraint Satisfaction problems since temporal, resource and many other kinds of constraints must be respected in most real life problems.

@@

\begin{figure}
\centering
\includegraphics[scale=0.35]{figs/EUROPA-Architecture.jpg}
\caption{\small EUROPA's Architecture}
\label{fig:europa-architecture}
\vskip+0.1cm
\end{figure}
